---
title: "NFDI4Objects Umfrageauswertung"
author:
  - Sophie C. Schmidt:
      email: sophie.schmidt@dainst.org
      institute: [DAI]
      correspondence: true
institute:
  - DAI: Deutsches Archäologisches Institut
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

#Datengrundlage

Daten als csv bekommen und IPs etc entfernt.

Zusammenfassungen der Fragen als  als xls bekommen.

```{r}
library(readxl)

```


# Empfundener Mehrwert N4O
```{r}
pers_mehrwert_N40 <- read_xls("../data/raw_data/statistic-survey615517_zusammenfassungen.xls", sheet = "persönlichMehrwertN4O") 

```

Word Cloud zur Visualisierung

```{r}
library("tm")
library("SnowballC")
library("wordcloud")


library(RColorBrewer)

docs <- Corpus(VectorSource(pers_mehrwert_N40))

docs$meta$language <- "de"

inspect(docs)

toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")
docs <- tm_map(docs, toSpace, "\\n")

# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
#docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, stopwords("german"))


# Remove your own stop word
# specify your stopwords as a character vector
docs <- tm_map(docs, removeWords, c("dass")) 
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
#docs <- tm_map(docs, stemDocument, "german") #vvlt keine gute idee?

# Document matrix is a table containing the frequency of the words. 
# Column names are words and row names are documents. 
# The function TermDocumentMatrix() from text mining package can be used as follow :
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 100)

col <- rev(brewer.pal(11, "RdYlGn"))

set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=100, random.order=FALSE, rot.per=0.35, 
          colors=col)

```


# 

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References 

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
